### 2024-02-18 paper_sisc_first_revision/localpsf.tex
updated section 7.1

\section{Preliminaries}

@@

\subsection{Example 1: Spatially variant blur}
\label{sec:frog}

Before delving into technical details, we provide an overview of the method. Along the way, we illustrate steps using a spatially variant blur example, in which the integral kernel is given as follows:
\begin{equation}
\label{eq:frog_kernel}
\Phi(y,x) = (1 - a f(y,x)) g(x) \exp \left(-\frac{1}{2}h^T(y,x) C^{-1} h(y,x)\right).
\end{equation} 
Here, $h(y,x) = R(\theta(x)) (y-x)$, $R(\theta(x))$ is the 2D rotation matrix by angle $\theta(x) = (x^1 + x^2) \pi / 2$, $C = L^2 \operatorname{diag}(c_1, c_2)$, $g(x) = x^1(1-x^1)x^2(1-x^2)$,  and $f(x,y) = \cos\left(p^1(y,x) / \sqrt{c_1 / 2.0}\right) \sin\left(p^2(y,x) / \sqrt{c_2 / 2.0}\right)$ for some constants $a, L, c_1, c_2$. In this section we use $a=1.0$, $L^2=1.0$, $c_1=0.01$, and $c_2=0.0025$. Using this kernel, the impulse response $\phi_x$ is a bumpy blob that is centered near $x$, and is rotated and scaled in a manner that depends on $x$ (see Figure \ref{fig:frog1}). The constant $L$ controls how wide the blob is, and $a$ controls the bumpiness. With $a=0$, $\phi_x$ is a Gaussian. As $a$ increases, $\phi_x$ becomes more bumpy. When $a > 1$, the integral kernel contains negative values, which violates the assumptions of our method. Note that for this operator, using our method is unnecessary because entries of the kernel are given directly via a formula. The purpose of this example is to illustrate the method using an operator which is known exactly and may be easily visualized.

>>>>

\section{Preliminaries}
\label{sec:prelims}

@@

\subsection{Example 1: Spatially varying blurring problem}
\label{sec:frog}

Here we define the PDE-free spacially varying blurring problem, used
in Sections~\ref{sec:intro} and~\ref{sec:prelims} for visual
illustration of various stages and aspects of the proposed method.  To
study the influence of the presence of negative numbers in the
integral kernel, i.e., the robustness of the proposed method to
violations of the non-negative kernel assumption discussed in
Section~\ref{sec:impulse_response_2}, this example is set up so that
the impulse response, $\phi_x$, corresponding to the integral kernel
is a bumpy blob that is centered near $x$, and is rotated and scaled
in a manner that depends on $x$ (see Figure
\ref{fig:frog_kernel_impulse_responses}). The closed form expression
of the integral kernel is given by
%
%Before delving into technical details, we provide an overview of the
%method. Along the way, we illustrate steps using a spatially variant
%blur example, in which the integral kernel is given as follows:
%\begin{equation}
%\label{eq:frog_kernel}
%\Phi(y,x) = (1 - a f(y,x)) x^1(1-x^1)x^2(1-x^2) \exp \left(-\frac{1}{2}h^T(y,x) C^{-1} h(y,x)\right).
%\end{equation}
%Here, $h(y,x) = R(\theta(x)) (y-x)$, $R(\theta(x))$ is the 2D rotation
%matrix by angle $\theta(x) = (x^1 + x^2) \pi / 2$, $C = L^2
%\operatorname{diag}(c_1, c_2)$, $g(x) = x^1(1-x^1)x^2(1-x^2)$, and
%$f(x,y) = \cos\left(p^1(y,x) / \sqrt{c_1 / 2.0}\right)
%\sin\left(p^2(y,x) / \sqrt{c_2 / 2.0}\right)$ for some constants $a,
%L, c_1, c_2$. In this section we use $a=1.0$, $L^2=1.0$, $c_1=0.01$,
%and $c_2=0.0025$.
%
\begin{align}
\label{eq:example_frog_kernel}
\Phi(y,x) = (1 - a f(y,x)) g(x) \exp \left(-\frac{1}{2}(h(y,x)^T
C^{-1} h(y,x) \right),
\end{align}
where $f(y,x) = \cos\left(h^1(y,x) / \sqrt{c_1 /
  2}\right)\sin\left(h^2(y,x) / \sqrt{c_2 / 2}\right)$, with
$h^i(y,x)$ the $i^{th}$ component of $R(\theta(x)) (y-x)$, with
$R(\theta(x))$ a two-dimensional rotation matrix by angle $\theta(x) =
(x^1 + x^2) \pi / 2$, $g(x) = x^1(1-x^1)x^2(1-x^2)$, and $C = L^2
\operatorname{diag}(c_1, c_2)$. The constant $L$ controls how wide the
blob is (hence the support of the impulse response), $a$ controls the
magnitude of the bumps, and $(c_1, c_2)$ control the width of the
Gaussian. We note that when $a=0$, $\phi_x$ is a Gaussian, as $a$
increases, $\phi_x$ becomes more bumpy. For instance, when $a > 1$,
the integral kernel contains negative values, which violates the
Assumption 3 (see Section~\ref{sec:conditions_2}).

%The impulse response $\phi_x$ corresponding to this kernel is a bumpy
%blob that is centered near $x$, and is rotated and scaled in a manner
%that depends on $x$ (see Figure
%\ref{fig:frog_kernel_impulse_responses}). The constant $L$ controls
%how wide the blob is (hence the support of the impulse response), and
%$a$ controls the magnitude of the bumps.

%Note that for this
%operator, using our method is unnecessary because entries of the
%kernel are given directly via a formula. The purpose of this example
%is to illustrate the method using an operator which is known exactly
%and may be easily visualized.
